Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-16 review_article.Rmd
GOINO maps as a storage device notes

<!--
@GOINO major geographic storage device; map reading and map interpretation have been the basic methods of retrieval and analysis.
Geography’s interests are in spatial distributions and associations, in areal differentiation
and in spatial processes. All of these interests demand information that is geographically
ordered. Geographically ordered data are those data which have their locational
coordinates preserved.

Certain limitations to the standard graphic techniques have also become apparent, however.
They are slow, and do not permit instant retrieval of information. They are untrustworthy when interpretations of spatial association are needed; there are both severe physiological and psychological constraints on our abilities to assess correlations of
spatial distributions visually.

There are six potential benefits to geographic research from computer-connected data banks in which the data have proper locational referents. These come under the general headings of mapping, partitioning and aggregation, merging of data systems, transformations of geographic spaces, descriprive statistics, and intermediate analysis.

@@

@@

>>>>

@@

<!--
@GOINO major geographic storage device; map reading and map interpretation have been the basic methods of retrieval and analysis.
Geography’s interests are in spatial distributions and associations, in areal differentiation
and in spatial processes. All of these interests demand information that is geographically
ordered. Geographically ordered data are those data which have their locational
coordinates preserved.
-->

@@

<!--
Certain limitations to the standard graphic techniques have also become apparent, however.
They are slow, and do not permit instant retrieval of information. They are untrustworthy when interpretations of spatial association are needed; there are both severe physiological and psychological constraints on our abilities to assess correlations of spatial distributions visually.
